Source Summaries

### 2020-03-02 paper/sourceSummaries/summary5.tex
fixed pdf issues
summary5 first commit

\noindent
\subsection{Title}

@@

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
%\bibentry{filizzola2018security}

@@

\noindent
Main Idea

@@

\noindent
Theory

@@

\noindent
Method

@@

\noindent
Findings

@@

\noindent
Future Directions

>>>>

\noindent
\subsection{{O}utput {C}haracteristics and {C}ircuit {M}odeling of {W}iegand {S}ensor}

@@

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
\bibentry{Sun_Yamada_Takemura_Wiegand}

@@

\noindent
In this paper the authors take a deep dive into the circuit design and output characteristics of a sensor using weigand technology as well as propose a new design for the sensor to make it more efficient.

@@

\noindent
Game Theory is the underlying theory behind this paper as the authors propose a situation where a wiegand sensor can use its own pulse voltage as a power source as a win

@@

\noindent
The authors first measured the pulse voltage from a test sensor they had in their lab, they then created an equivalent electrical circuit to generate the same numbers generated from the weigand, they then used this circuit to calculate the amount of voltage needed to run the device consistantly and determine whether or not their idea was sound. They also used matlab/simulink simulation to help with this process.

@@

\noindent
The authors found that the pulse voltage created by the internals of the wiegand sensor were uniform enough to be used for energy harvesting, and that the simulation numbers agreed with the real world behavior reflected by the test circuit they created.

@@

\noindent
The authors propose further testing of their design at abnormal temperatures as they state that the device will behave differently depending on the outside air temperature where the circuit is being operated.
